Nail: A practical interface generator for binary formats

### 2014-04-01 paper/intro.tex
add a challenge (maybe) about cconstraints in the input format

A promising approach to avoid such vulnerabilities is to specify a
precise grammar for the input data format, and to use a parser generator,
such as {\tt lex} and {\tt yacc}, to synthesize the input processing
code.  Developers that use a parser generator will not need to write
error-prone input processing code on their own, and as long as the
parser generator is bug-free, the application will be safe from input
processing vulnerabilities.  Unfortunately, applying this approach in
practice, using state-of-the-art parser generators, requires addressing
several challenges.

@@

A similar problem occurs when the programmer wants to generate output.
Even though not all programs may use the same format for output as they
do on input, different programs might use the same format for input and
output and re-using the same grammar is a good way to save engineering
effort and reduce parser differentials.  Some parser generators, e.g.
Boost.Spirit,\footnote{\url{http://www.boost.org/doc/libs/1_55_0/libs/spirit/doc/html/index.html}}
allow the same grammar to be re-used for generating output from the
intermediate representation.  However, those generators require a new set
of semantic actions to be written, even though the relationship between
grammar and intermediate model was already expressed in the actions for
the parser.

>>>>

A promising approach to avoid such vulnerabilities is to specify
a precise grammar for the input data format, and to use a parser
generator, such as {\tt lex} and {\tt yacc}, to synthesize the input
processing code.  Developers that use a parser generator do not need
to write error-prone input processing code on their own, and as long
as the parser generator is bug-free, the application will be safe from
input processing vulnerabilities.  Unfortunately, applying this approach
in practice, using state-of-the-art parser generators, still requires
too much manual programmer effort, making it error-prone, as we describe
next.

@@

Second, data formats can have constraints XXX todo.

Third, applications often need to produce output in the same
format as their input---for example, applications might both
read and write files, or both receive and send network packets.
Most parser generators just focus on parsing an input, rather
than producing an output, thus requiring the programmer to manually
construct outputs, which is error-prone.  Some parser generators, such as
Boost.Spirit,\footnote{\url{http://www.boost.org/doc/libs/1_55_0/libs/spirit/doc/html/index.html}}
allow reusing the grammar for generating output from the internal
representation.  However, those generators require yet another set of
semantic actions to be written, transforming the internal representation
into an AST\@.

This paper presents the initial design and implementation of Nail, a
parser generator that greatly reduces the programmer effort required to
use a grammar-based parser.  Nail addresses the above three challenges
with several key ideas.  First, Nail XXX todo.
